%-------------------------
% Resume in Latex
% Author : Alireza Manashty
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://manashty.wordpress.com/}{\Large Alireza Manashty}} & \href{mailto:a.r.manashty@gmail.com}{a.r.manashty@gmail.com}\\
Lead Data Scientist | PhD Candidate &  \href{http://linkedin/in/manashty/}{linkedin.com/in/manashty}\\
11-21 Christopher Crt,& \href{http://github.com/manashty}{github.com/manashty} \\
St. John, NB, E2K 4L4, Canada  & (506) 898-2227 \\
\end{tabular*}

\section{Summary}
7+ years of practical problem solving using machine learning. Helped federal and provincial government and tech companies (e.g., Dell EMC) by providing predictive data science consultant. Awarded Microsoft MVP in Azure.
      \resumeItemListStart
        \resumeItem{Full-stack data scientist}
          {Provided complete solutions for problems, from business discovery, solution design, data acquisition (Sql/NoSql), modeling (R, Python, Java/C\#, web), visualization, and deployment (local/cloud services)}
              \resumeItem{Instructor \& professional trainer}
          {7 years of teaching main CS undergraduate courses. Data science trainer.}
      \resumeItemListEnd
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
          {Ph.D. in Computer Science |  University of New Brunswick}{2014 -- 2018 (Pending defense)}
      {Predictive Analytics in Health Monitoring (Thesis); GPA 4.1/4.3}{NB, Canada}
      \resumeItemListStart
        \resumeItem{Contributions}
          {Mapped years of multivariate sporadic health data into 32 elements for anomaly forecasting by developing a mathematical model. Enabled human fall forecasting upto 15s before the fall using LSTM.}
      \resumeItemListEnd
%            {University of New Brunswick}{NB, Canada}

    \resumeSubheading
          {M.Sc. in Computer Engineering (AI) |  Shahrood University of Technology}{2010 -- 2012}
      {Sign Language Recognition using ToF depth cameras (Thesis); GPA 3.7/4 (Rank 1/20)}{}
            \resumeItemListStart
        \resumeItem{Coursework}
          {Machine Learning; Statistical Pattern Recognition; Computer Vision; Neural Networks; Fuzzy; AI}
      \resumeItemListEnd

          \resumeSubheading
          {B.Sc. in Software Engineering |  Razi University}{2006 -- 2010}
      {Smart House Remote Monitoring System (Thesis); GPA 3.7/4 (Rank 3/61)}{}

%    \resumeSubheading
 %     {Birla Institute of Technology and Science}{Pilani, India}
  %    {Bachelor of Engineering in Electrical and Electronics;  GPA: 3.66 (9.15/10.0)}{Aug. 2008 -- July. 2012}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
          {Data Scientist}{June 2018 - Present}
      {Department of Health, Government of New Brunswick}{Fredericton, Canada}
      \resumeItemListStart
                \resumeItem{Prediction}
          {Forecasting physician retirements 5 years in-advance using machine learning techniques.}
        \resumeItem{NB Health Data}
          {Converting 10 years of diagnosis free-text to ICD-10 code using NLP and Deep Learning.}

%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines, as well as a set of language-specific SDKs for constructing pipelines and runners.}
      \resumeItemListEnd

    \resumeSubheading
          {Lead Data Scientist (Consultant)}{June 2018 - Present}
      {IPSNP Computing Inc.}{Saint John, Canada}
            \resumeItemListStart
          \resumeItem{Prediction}
          {Forecasting hospital admission and bed requirements for the largest emergency department in NB.}
        \resumeItem{Forecasting}
          {Predicting workers back-to-work probability upon admission for WorkSafeNB}
      \resumeItemListEnd
    \resumeSubheading
      {Data Scientist}{Feb 2018 - June 2018}
      {CGS (Computer Generated Solutions) Canada}{Saint John, Canada}
      \resumeItemListStart
        \resumeItem{Dell EMC Data Science Train the Trainer (TTT) Instructor}
          {Trained the Dell EMC's trainers for Data Science \& Big Data Analytics v2 course using +500 slides and 12 labs over 5 days (40 hours). Reviewed and updated the learning materials and labs. Topics included statistical and analytical theories \& big data tools.}
        \resumeItem{Virtual Big Data Lab development}
          {Created/Tested/Deployed the lab environment for Dell EMC DSBDAv2 course using VMware ESXi server for Hadoop, Spark, R Server, and Greenplum database (4 virtual machines).}
      \resumeItemListEnd

    \resumeSubheading
	  {University Instructor, Research, and Teaching Assistant}{Jan 2014 - June 2018}
      {University of New Brunswick}{New Brunswick, Canada}
      
%      {Research and Teaching Assistant}{Jan 2012 - Dec 2013}
%      {Georgia Institute of Technology}{Atlanta, GA}

      \resumeItemListStart
        \resumeItem{Lecturer and Lab Instructor}
          {Taught 16 Credits \& 8 Lab hours for over 150 undergrad and graduate students.} \resumeItem{Courses}{ Database Management Systems II | Operating Systems I | Computer Networking | Systems Software Development | C++ for Java Programmers | Honour's Project | Technical Report}
                  \resumeItem{Graduate Research/Teaching Assistant}{Conducting research in Health Predictive Analytics @ Fall Lab}
         \resumeItem{Diploma of University Teaching}
          {Passed the teaching training and received the certificate, UNB, May 2015}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{More}
  \resumeSubHeadingListStart
    \resumeSubItem{Microsoft Most Valuable Professional (MVP) in Azure}
      {Awarded in 2017 for community contributions.}
    \resumeSubItem{Microsoft Azure Research}
      {Awarded a total of \$57,000 of Microsoft Azure Subscription for academic use.}
    \resumeSubItem{Programming Languages | Skills}
      {C\#, Java, Python, R, C++| Predictive Analytics, R\&D, Management}
    \resumeSubItem{MITACS Accelerate PhD Fellowship Intern (Java) }
      {Awarded \$90,000 industry fellowship, IPSNP Inc., 2014}            \resumeSubItem{Publication list (Google Scholar)}
      {\href{https://scholar.google.ca/citations?user=oTFzSi0AAAAJ&hl=en}{https://scholar.google.ca/citations?user=oTFzSi0AAAAJ}}            
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\begin{comment}
DATA SCIENCE: DEEP LEARNING, MACHINE LEARNING, PATTERN RECOGNITION
Techniques: Deep Learning, Machine Learning, Statistical Pattern Recognition, Data Visualization

Algorithms:  CNN, RNN, LSTM, DBN, GBM, Random Forests, SVM, Bayes, ANN, KNN, K-Means, Fuzzy Systems

Tools/Languages: Python (Jupyter), R, Tensorflow, Matlab, Microsoft CNTK (Cognitive Toolkit), H2O, Weka, Accord.Net, OpenCV, ALGLib, EmguCV

DATABASE AND CLOUD: MICROSOFT AZURE, GOOGLE CLOUD, SQL, NOSQL, MONGODB, DOCUMENT DB

Microsoft Azure, Docker, IoT Hub, DocumentDB, SignalR, EventHub, StreamAnalytics, Microservices, Mobile Services
MSSQL, MySQL, PostgreSQL, Oracle, Access NOSQL: DocumentDB, MongoDB

Data Visualization, Microsoft Power BI, D3.js

SOFTWARE ENGINEERING		SCRUM, AGILE, DEVOPS, ETL, GIT, SVN
Project Management, Software Design, UI Prototyping, UML, Unit Testing, Database Entity Relations, Deployment and licensing, OOP, Parallel Programming

PROGRAMMING: PYTHON 3.X, C# .NET (C# 7), JAVA, VISUAL C++/VB .NET, C/C++, OPENGL, XNA
Expert C# Programmer since 2006 (Robotics Soccer Simulator and game planner)
Designed and developed smart house control system (Web/mobile and desktop)
ARMrayan Mobile CMS (Award winning, designing and outputting J2ME apps from Windows with a single click)
Designed and developed software licensing locks, distributed, sold and supported for 4 years

WEB: ASP.NET, JAVA, MICROSERVICES, WEB-API, RESTFUL SERVICES, HTML5, BOOTSTRAP, ANGULARJS, JQUERY, NODEJS, CSS, JAVASCRIPT, AJAX, WEB SERVICES (REST, WCF, RDF, SADI)
Designed developed several client and admin websites
Designed and developed a scientific journal management system with Telerik, SQL and ASP.Net
Experience with PHP Frameworks. Been certificate judge for PHP certification exam.

MOBILE:    			WINDOWS 10/8.1 APP STORE, WINDOWS PHONE, ANDROID, RASPBERRY PIE
[Android/Google Play] Publisher and selling in Google Play. Designed and led a student team to develop an app.
 [Windows 8.1/10 App Store and Windows Phone 8.1] Has around 10 apps published in store now
[Windows 10 IoT Core] Experience with universal apps for Raspbery Pie 2/3 via Windows 10 Universal apps and GPIO
[Windows Phone] Designed Smart House Simulator in mobile
[J2ME] Designed and developed two award-winning mobile content management system (ARMrayan Mobile CMS)
Coined the term Mobile CMS for the first time in an international conference. 
SEMANTIC WEB: SPARQL, RDF(S), Google Refine, Protégé, RDF123

VIRTUALIZATION AND NETWORKING
HyperV, VMWare, Remote Desktop, Powershell, Windows Server, Authentication, Security

Thesis Summary:
Predictive analytics in healthcare can prevent patients’ emergency health conditions, and reduce costs in the long term. The motivation of my research is to model a patients' long-term history to not only detect, but to forecast anomalies. My model (called as Life Model (LM)) is used to predict and forecast 32 months mortality of 34,000 ICU patients. LM is also used to forecast human fall up to 14 seconds in advance. With LM, years of patients' data can be summarized in 32 elements so it can easily be used to map history to future and forecast events years before happening. 

Data Science Course:
https://education.emc.com/guest/campaign/data_science.aspx#course1


Why data science?
I enjoy helping companies solve predictive problems by providing answers to questions they may even have problem asking. The research in data science and deep learning is moving fast, however, with the data currently available, many problems can already be solved. Many of the predictive solutions have a direct impact on people. Reducing wait times, providing intelligent services, and automating manual tasks are all positive activities that can improve the life of the individuals around the world. Such improvements directly and indirectly help the tech industries to thrive as well, as they are servicing millions of those happier individuals each day. Being part of this process is an exciting and meaningful journey for me.

\end{comment}
\end{document}
